Yeast RNA-seq 48 sample simulation study

### 2018-02-15 datasets/RNA-Seq/yeast48-replicates-benchmarkFDR.Rmd
Remove extraneous code chunk

```{r}
  mat <- ( assays( de5[[1]] )[["qvalue"]] < 0.1 )
  dfCov <- data.frame(
    covariate = sizesAll,
    methods=factor( rep( names( allLenghts ), sapply( allLenghts, length ) ), 
                    levels=names(allLenghts)  ) )
  pl <- ggplot( dfCov, aes( methods, trans(covariate), col=methods) ) +
    geom_boxplot( ) + theme(legend.position="top", 
                            axis.text.x=element_blank(), 
                            legend.direction="vertical") +
    labs(col="", y="Covariate", x="") + guides(color=guide_legend(ncol=2))
  pl
}

res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.20, 0.01))

>>>>

```{r}
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.20, 0.01))
